---
title: "p8105_hw5_jz3573"

output: github_document

author: Jiangyuan Zhu 

date: "2023-11-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(tools)
library(ggplot2)

```

# Question 2
## Make a dataframe 
read the names of files.
```{r read the name of files }
path_list=list.files(path = "./data" , full.names = TRUE ) 
```

input the context
```{r input the context}
context=purrr::map(path_list, read.csv) %>% 
bind_rows()  %>% 
round(digits = 2)
```

input the names
```{r input the names}
name_df=list.files(path = "./data")  %>% 
  file_path_sans_ext %>% 
  data_frame()

```

combine the files and add a column name
```{r combine the files and add a column name }
full_df = bind_cols(name_df, context) 
  
names(full_df) [1]="id"

```

make it a computer-readable dataframe
```{r make it a computer-readable dataframe}
full_tidy_df = 
  pivot_longer(
    full_df, 
    week_1:week_8,
    names_to = "week", 
    names_prefix = "week_",
    values_to = "index")
```

## Make a plot
```{r }
full_tidy_df %>% 
ggplot(aes(x=week , y=index, group = id, color = id))  + geom_line()

```


According to the plot, the experience groups have higher value than the control groups over weeks. 


# Problem 3 
## create 5000 datasets
```{r create 5000 datasets}
set.seed(1)

output = vector("list", 5000)
for (i in 1:5000) {
  output[[i]] = rnorm(30,0,5 )
}

```

## create a dataframe save 5000 μ̂ and p-value

```{r create a dataframe  save 5000 μ̂ and p-value }
output_si = vector ("list", 5000)

for (i in 1:5000){
output_si[[i]]= t.test(output[[i]], conf.level = 0.05 ) %>%
  broom::tidy() %>% 
  select(estimate, p.value) 
}

sim_result_0 = bind_rows(output_si)

set.seed(1)
```


## repeat the procedure for μ={1}
```{r repeat the prcedure for μ={1} }
output = map(1:5000, ~ rnorm(30,1,5)  )
             
for (i in 1:5000){
output_si[[i]]= t.test(output[[i]], conf.level = 0.05 ) %>%
  broom::tidy() %>% 
  select(estimate, p.value) 
}

sim_result_1 = bind_rows(output_si)

set.seed(1)


```

## create a function 
```{r}
sim_power = function(mu) {
  
  data = tibble(
    x = rnorm(n = 30, mean = mu, sd = 5)
  )
  
  output = data %>%  
    t.test() %>% 
    broom::tidy() %>% 
    select(estimate, p.value) 
}

sim_power_results = expand_grid(
  mu_df = c(0, 1, 2, 3, 4, 5, 6), 
  iteration = 1:5000
) %>% 
  mutate(
    estimate = map(mu_df, sim_power)
  ) |> 
  unnest(estimate)
```



